My Data Literacy Project\\ (Replace this with your Project Title)

### 2024-01-25 doc/DataLiteracyStudentProject/paper.tex
Include a new fig
Visualization of mapping
First implementation

\begin{icmlauthorlist}
\icmlauthor{Abdullah Abdul-Latif}{equal,first}
\icmlauthor{Lisa-Maria Fritsch}{equal,second}
\icmlauthor{Paul Kaifler}{equal,third}
\icmlauthor{Maximilian Schnitt}{equal,fourth}
\end{icmlauthorlist}

% fill in your matrikelnummer, email address, degree, for each group member
\icmlaffiliation{first}{Matrikelnummer 12345678, first.last@student.uni-tuebingen.de, MSc Machine Learning}
\icmlaffiliation{second}{Matrikelnummer 12345678, first.last@student.uni-tuebingen.de, MSc Computer Science}
\icmlaffiliation{third}{Matrikelnummer 12345678, first.last@student.uni-tuebingen.de, MSc Media Informatics}
\icmlaffiliation{fourth}{Matrikelnummer 6040570, maximilian.schnitt@student.uni-tuebingen.de, BSc Computer Science}

@@

%Put your abstract here. Abstracts typically start with a sentence motivating why the subject is interesting. Then mention the data, methodology or methods you are working with, and describe results. 
\begin{abstract}
As often mentioned in the news and in the daily life, people suggest that a higher expected salary is a strong pull factor for students 
choosing their subject. We were curious if this is particullarily true for the scientific based subjects, because a majority of them have a 
pretty high expected salary. We used the students data from the \href{https://uni-tuebingen.de/einrichtungen/verwaltung/iv-studierende/studierendenabteilung/statistiken/}{Statistics University of Tübingen}, 
the high-school graduates data from the \href{https://www.statistik-bw.de/BildungKultur/SchulenAllgem/LRt0302.jsp}{Statistisches Landesamt Baden-Württemberg}
and also the salary data from 2005 to 2023 from the \href{https://www-genesis.destatis.de/genesis//online?operation=table&code=62321-0001&bypass=true&levelindex=0&levelid=1702307320529#abreadcrumb}{Deutsches Statistisches Bundesamt}.
We used a vector autoregressive model, to build a time series forecast and analysed the outcomes to find an optimal configuration for this type of model in our context.
\textcolor{red}{result.}
%Motivate the problem, situation or topic you decided to work on. 
% Describe why it matters (is it of societal, economic, scientific value?). 
% Outline the rest of the paper (use references, e.g.~to \Cref{sec:methods}: 
% What kind of data you are working with, how you analyse it, and what kind of conclusion you reached. 
% The point of the introduction is to make the reader want to read the rest of the paper.

@@

After we ensured, that our data is stationary, we used a PACF plot to find lags which could be statistically significant. 
The main reason why we choose PACF in contrast to ACF is that we only want to look at direct influences from $S_{n-1}$ to $S_{n}$ and not from $S_{n-3}$ to $S_n$.
\begin{figure}[H]
    \centering
    \includegraphics[width=\linewidth,height=\textheight, keepaspectratio]{fig/pacf_plot.pdf}
    \caption{PACF Plot for our VAR Model}
    \label{fig:enter-label}
\end{figure}
\textcolor{red}{// CONCLUSION FOR PACF // }\\

@@

>>>>

\begin{icmlauthorlist}
\icmlauthor{Abdallah Abdul-Latif}{equal,first}
\icmlauthor{Lisa-Maria Fritsch}{equal,second}
\icmlauthor{Paul Kaifler}{equal,third}
\icmlauthor{Maximilian Schnitt}{equal,fourth}
\end{icmlauthorlist}

% fill in your matrikelnummer, email address, degree, for each group member
\icmlaffiliation{first}{Matrikelnummer 5977981, abdallah.abdul-latif@student.uni-tuebingen.de, MSc Computer Science}
\icmlaffiliation{second}{Matrikelnummer 12345678, first.last@student.uni-tuebingen.de, MSc Computer Science}
\icmlaffiliation{third}{Matrikelnummer 12345678, first.last@student.uni-tuebingen.de, MSc Media Informatics}
\icmlaffiliation{fourth}{Matrikelnummer 6040570, maximilian.schnitt@student.uni-tuebingen.de, BSc Computer Science}

@@

%Put your abstract here. Abstracts typically start with a sentence motivating why the subject is interesting. Then mention the data, methodology or methods you are working with, and describe results. 
\begin{abstract}
As often mentioned in the news and in the daily life, people suggest that a higher expected salary is a strong pull factor for students 
choosing their subject. We were curious if this is particullarily true for the scientific based subjects, because a majority of them have a 
pretty high expected salary. We used the students data from the \href{https://uni-tuebingen.de/einrichtungen/verwaltung/iv-studierende/studierendenabteilung/statistiken/}{Statistics University of Tübingen}, 
the high-school graduates data from the \href{https://www.statistik-bw.de/BildungKultur/SchulenAllgem/LRt0302.jsp}{Statistisches Landesamt Baden-Württemberg}
and also the salary data from 2005 to 2023 from the \href{https://www-genesis.destatis.de/genesis//online?operation=table&code=62321-0001&bypass=true&levelindex=0&levelid=1702307320529#abreadcrumb}{Deutsches Statistisches Bundesamt}.
We used a vector autoregressive model, to build a time series forecast and analysed the outcomes to find an optimal configuration for this type of model in our context.
\textcolor{red}{result.}
%Motivate the problem, situation or topic you decided to work on. 
% Describe why it matters (is it of societal, economic, scientific value?). 
% Outline the rest of the paper (use references, e.g.~to \Cref{sec:methods}: 
% What kind of data you are working with, how you analyse it, and what kind of conclusion you reached. 
% The point of the introduction is to make the reader want to read the rest of the paper.
\end{abstract}

@@

After we ensured, that our data is stationary, we used a PACF plot to find lags which could be statistically significant. 
The main reason why we choose PACF in contrast to ACF is that we only want to look at direct influences from $S_{n-1}$ to $S_{n}$ and not from $S_{n-3}$ to $S_n$.
\begin{figure}
    \includegraphics{fig/pacf_plot.pdf}
    \caption{PACF Plot for our VAR Model}
\end{figure}
\textcolor{red}{// CONCLUSION FOR PACF // }\\

@@

\begin{figure*}
    \includegraphics{fig/params.pdf}
    \caption{This is a figure caption. Write this, if we end up using that fig ;-)}
\end{figure*}
